Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-22 paper/ijcai/paper.tex
adjust margins
more fixes

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to evaluate the effects of combining \ds{} with \sfl{}. We suspect
that several highly suspicious components---often involved in failing,
but seldom in passing test runs---may be unrelated to the bug. With
the aforementioned combination, such components could be located and
their suspiciousness reduced.  This study also discusses the practical
impact of the \ds{} key limitation---the risk of missing faulty
statements. Results indicate that \ds{} misses faulty statements in
only 9\%\comments{(23 misses)} of the 260 cases\Mar{we are using
  \numFaults{} in the paper. please, revise and use macros.} and that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves on average
the diagnostic accuracy by \avgImprov\ in 51\% of the cases. To sum,
we found that the \ds{}-\sfl{} combination was practical and effective
and encourage new \sfl{} techniques to be evaluated against that
optimization.
\end{abstract}

@@

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the issues from prior work. The study we conducted involves
\numFaults{}\Mar{check} faults from \numPrograms{}\Mar{check}
different programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. The study covers the following
research questions:

@@

We used the \dfj{} benchmark in our experiments~\cite{just-defects4j-issta2014}.
This benchmark includes six different subjects and \numFaults{} faults (Table
\ref{tab:df4j}). \lang{} is a library that provides a set of helper utilities
for the {\small\texttt{java.lang}} API. \cmath{} is a lightweight library of
self-contained mathematics and statistics components. The \closure{} is a
toolset for turning JavaScript files into smaller scripts for faster download
and execution in the browser. \chart{} is a Java library for creating charts.
\jtime{} is a lightweight library that aims to replace the default Java
{\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is a
mocking testing framework.

@@

\begin{figure}[h]
	\vspace{-1.5cm}

		\centering
		\includegraphics[width=0.42\textwidth]{figures/defects4j.pdf}
		\vspace{-1cm}
		\caption{Faults of omissions' distribution}
		\label{fig:foos}
\end{figure}

@@

As observed in~\ref{table:fsws}, \combpar{k}
finds the faulty statements faster than \sfl{}$^{k}$.

We observe that $33$ of the $260$ faulty versions do not include the
faulty statements in the slicer report after slicing.

>>>>

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to evaluate the effects of combining \ds{} with \sfl{}. We suspect
that several highly suspicious components---often involved in failing,
but seldom in passing test runs---may be unrelated to the bug. With
the aforementioned combination, such components could be located and
their suspiciousness reduced.  This study also discusses the practical
impact of the \ds{} key limitation---the risk of missing faulty
statements. Results indicate that \ds{} misses faulty statements in
 12.7\%\comments{(33 misses)} of the \numFaults{} cases and that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves on average
the diagnostic accuracy by \avgImprov\ in 51\% of the cases. To sum,
we found that the \ds{}-\sfl{} combination was practical and effective
and encourage new \sfl{} techniques to be evaluated against that
optimization.
\end{abstract}

@@

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the issues from prior work. The study we conducted involves
\numFaults{} faults from \numPrograms{}
different programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. The study covers the following
research questions:

@@

We used the \dfj{} benchmark in our experiments~\cite{just-defects4j-issta2014}.
Originally, this benchmark includes six different subjects and 395 faults (Table
\ref{tab:df4j}). \lang{} is a library that provides a set of helper utilities
for the {\small\texttt{java.lang}} API. \cmath{} is a lightweight library of
self-contained mathematics and statistics components. The \closure{} is a
toolset for turning JavaScript files into smaller scripts for faster download
and execution in the browser. \chart{} is a Java library for creating charts.
\jtime{} is a lightweight library that aims to replace the default Java
{\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is a
mocking testing framework.

@@

\begin{figure}[h]
  \vspace{-0.5cm}

		\centering
		\includegraphics[width=0.42\textwidth]{figures/defects4j.pdf}
		\vspace{-0.75cm}
		\caption{Faults of omissions' distribution}
		\label{fig:foos}
\end{figure}

@@

We observed that $33$ of the $260$ faulty versions do not include the
faulty statements in the slicer report after slicing.
As observed in~\ref{table:fsws}, \combpar{k}
finds the faulty statements faster than \sfl{}$^{k}$.
